---
title: "Discipline figures"
format: pdf
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(colorspace)
library(patchwork)

theme_set(theme_minimal())

df <- readxl::read_excel("Full_data_2024_04_02.xlsx")

relevant_data <- df %>% 
  # read_excel imports an empty row for some reason
  filter(!is.na(item_id)) %>% 
  mutate(publication_year = str_extract(author_year, "\\d+")) %>% 
  select(article_id = item_id, frasc_top = `discipline_frascati_top-level`,
         frasc_2nd = `discipline_frascati_2nd-level`, publication_year) %>% 
  mutate(study_id = seq_along(article_id)) %>% 
  select(article_id, study_id, everything())

stopifnot(identical(nrow(relevant_data), 104L))
```


# Data issues

- The frascati top level is not delimineted with a semicolon in the last row, 
but with an "and".
- Same for article id 91550908, which uses a colon (,)
- Same issue with second level for article id 88008647
- Some second level frascati are misspelled
- Some first order codings are missing


# Fix the issues (except first order codings)

```{r}
relevant_fixed <- relevant_data %>% 
  mutate(frasc_top = str_replace_all(frasc_top, ",", ";") %>% 
           str_replace_all("(?<=Natural sciences) and (?=Medical)", "; "),
         frasc_2nd = str_replace_all(frasc_2nd, "Sciences", "sciences") %>% 
           str_replace_all(",", ";"))
```


# Split top level
```{r}
frasc_top_long <- relevant_fixed %>% 
  # we split by semicolon, but there is an error in the last row
  mutate(frasc_top_split = str_split(frasc_top, ";\\s")) %>% 
  unnest(frasc_top_split)
```


# Panel 3 - papers over time
```{r}
p3 <- frasc_top_long %>% 
  count(publication_year, frasc_top_split) %>% 
  ggplot(aes(publication_year, n, fill = frasc_top_split)) +
  geom_col(width = .75) +
  scale_fill_discrete_qualitative() +
  theme(legend.position = "top") +
  labs(x = NULL, y = "# of studied disciplines", fill = NULL)
p3
```
Need a disclaimer here about 2023: there was probably a cut-off in the data, not
a decrease in studies (in particular since social sciences is much smaller, 
which might be due to longer publication times?).

# Panel 1 - Frascati distribution overall
```{r, fig.width=5, fig.height=3}
p1 <- frasc_top_long %>% 
  ggplot(aes(fct_rev(frasc_top_split), fill = frasc_top_split)) +
  geom_bar(show.legend = FALSE, width = .75) +
  scale_fill_discrete_qualitative() +
  labs(x = NULL, y = "# of studied disciplines", fill = NULL) +
  coord_flip()
p1
```

# Panel 2 - Second order frascati
```{r}
frasc_2nd_long <- relevant_fixed %>% 
  # we split by semicolon, but there is an error in the last row
  mutate(frasc_2nd_split = str_split(frasc_2nd, ";\\s")) %>% 
  unnest(frasc_2nd_split) %>% 
  mutate(frasc_top_split = 
           case_when(
             !str_detect(frasc_top, ";") ~ frasc_top,
             frasc_2nd_split == "Clinical medicine" ~ "Medical and health sciences",
             frasc_2nd_split == "Health sciences" ~ "Medical and health sciences",
             frasc_2nd_split == "Basic medicine" ~ "Medical and health sciences",
             frasc_2nd_split == "Psychology and cognitive sciences" ~ "Social sciences",
             frasc_2nd_split == "Other social sciences" ~ "Social sciences",
             frasc_2nd_split == "Biological sciences" ~ "Natural sciences",
             TRUE ~ NA_character_
           ))
```

```{r, fig.width=7, fig.height=5}
p2 <- frasc_2nd_long %>% 
  count(frasc_2nd_split, frasc_top_split) %>% 
  ggplot(aes(fct_reorder(frasc_2nd_split, n, .fun = max), n, fill = frasc_top_split)) +
  geom_col(show.legend = FALSE, width = .75) +
  scale_fill_discrete_qualitative() +
  labs(x = NULL, y = "# of studied disciplines", fill = NULL) +
  coord_flip()
p2
```

# Joint figure
```{r, fig.width=10, fig.height=7}
(p1 + p2) / p3 + plot_annotation(tag_levels = "A") +
  plot_layout(guides = "collect") & 
  theme(legend.position = "none")
```

There are still issues in the raw data - some frascati top levels were omitted,
which is why the colouring in panel B is off (for example, article id 88009136
has only medical and health sciences as top level, but has biological sciences 
and basic medicine at the sublevel --> natural sciences is missing at the 
toplevel)
