---
title: "Discipline_figures"
format: html
---
```{r}
library(tidyverse)
library(colorspace)

theme_set(theme_minimal())

df <- readxl::read_excel("Full_data_2024_04_02.xlsx")

relevant_data <- df %>% 
  # read_excel imports an empty row for some reason
  filter(!is.na(item_id)) %>% 
  mutate(publication_year = str_extract(author_year, "\\d+")) %>% 
  select(article_id = item_id, frasc_top = `discipline_frascati_top-level`,
         frasc_2nd = `discipline_frascati_2nd-level`, publication_year) %>% 
  mutate(study_id = seq_along(article_id)) %>% 
  select(article_id, study_id, everything())

stopifnot(identical(nrow(relevant_data), 104L))
```


# Data issues

- The frascati top level is not delimineted with a semicolon in the last row, 
but with an "and".
- Same for article id 91550908, which uses a colon (,)


```{r}
frasc_top_long <- relevant_fixed %>% 
  # we split by semicolon, but there is an error in the last row
  mutate(frasc_top_split = str_split(frasc_top, "(;\\s|,\\s)|(?<=Natural sciences) and (?=Medical)")) %>% 
  unnest(frasc_top_split)
```


# Panel 3 - papers over time
```{r}
frasc_top_long %>% 
  count(publication_year, frasc_top_split) %>% 
  ggplot(aes(publication_year, n, fill = frasc_top_split)) +
  geom_col(width = .75) +
  scale_fill_discrete_qualitative() +
  theme(legend.position = "top") +
  labs(x = NULL, y = "# of studied disciplines", fill = NULL)
```
Need a disclaimer here about 2023: there was probably a cut-off in the data, not
a decrease in studies (in particular since social sciences is much smaller, 
which might be due to longer publication times?).

# Panel 1 - Frascati distribution overall
```{r, fig.width=5, fig.height=3}
frasc_top_long %>% 
  ggplot(aes(fct_rev(frasc_top_split), fill = frasc_top_split)) +
  geom_bar(show.legend = FALSE, width = .75) +
  scale_fill_discrete_qualitative() +
  labs(x = NULL, y = "# of studied disciplines", fill = NULL) +
  coord_flip()
```

# Panel 2 - Second order frascati
```{r}
frasc_2nd_long <- relevant_data %>% 
  # we split by semicolon, but there is an error in the last row
  mutate(frasc_2nd_split = str_split(frasc_2nd, "(;\\s|,\\s)|(?<=Natural sciences) and (?=Medical)")) %>% 
  unnest(frasc_2nd_split) %>% 
  mutate(frasc_top_split = 
           case_when(
             
           ))
```

```{r}
frasc_2nd_long %>% 
  ggplot(aes(fct_rev(frasc_2nd_split), fill = frasc_top)) +
  geom_bar(show.legend = FALSE, width = .75) +
  scale_fill_discrete_qualitative() +
  labs(x = NULL, y = "# of studied disciplines", fill = NULL) +
  coord_flip()
```

